\myTitle

### 2024-01-26 tex/body-text-of-paper.tex
working...

We sampled fish for the reference baselines from XX locations across California.
These locations included sites in the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley, the Klamath-Trinity basin in Northern California, and
3 rivers of the California coast (Russian, Eel, etc)
(Fig.~\ref{fig:map}).
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations represented in the reference 
baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included in the collections from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run. Abbreviations used in location names as folows: R. = River; Ck. = Creek; H. = Hatchery; NFH = National Fish Hatchery.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%
Collections in each location were separated into fish from the different run-timing ecotypes according
to a variety of criteria. The last vestiges of winter-run Chinook salmon are maintained at the Livingston
Stone National Fish Hatchery for supplementation (released as juveniles into the river) and as a captive broodstock;
sampling of this population was performed by hatchery staff during spawning. In Central Valley Rivers with both 
spring and fall ecotypes (i.e. Mill, Deer and Butte Creeks), previous research has documented distinct/disparate/unique
spawning times (Julian date) for each ecotype (REF?). As such, sampling targeted carcasses found in each of these 
rivers at times representative of their run-timing designation, which we were able to further verify using their genotypes
at the RoSA markers. At the time of sampling, only fall-run Chinook were found in the San Joaquin River. Run-timing 
designation at the Feather River Hatchery is more complicated but is managed at a fine-scale by hatchery practices, 
where early returning fish in May and April (expressing the Spring-run life history) are visibly tagged and re-released 
to the river. Subsequently n the Fall, when hatchery raceways are reopened, only fish with the visible tag are included
as Spring-run broodstock. Individual-based analysis

>>>>

We sampled fish for the reference baselines from XX locations across California.
These locations included sites in the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley, the Klamath-Trinity basin in Northern California, and
3 rivers of the California coast (Russian, Eel, etc)
(Fig.~\ref{fig:map}).
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations represented in the reference 
baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included in the collections from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run. Abbreviations used in location names as folows: R. = River; Ck. = Creek; H. = Hatchery; NFH = National Fish Hatchery.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%
Collections in each location were separated into fish from the different run-timing ecotypes according
to a variety of criteria. The last vestiges of winter-run Chinook salmon are maintained at the Livingston
Stone National Fish Hatchery for supplementation (released as juveniles into the river) and as a captive broodstock;
sampling of this population was performed by hatchery staff during spawning. In Central Valley Rivers with both 
spring and fall ecotypes (i.e. Mill, Deer and Butte Creeks), previous research has documented distinct/disparate/unique
spawning times (Julian date) for each ecotype (REF?). As such, sampling targeted carcasses found in each of these 
rivers at times representative of their run-timing designation, which we were able to further verify using their genotypes
at the RoSA markers. At the time of sampling, only fall-run Chinook were found in the San Joaquin River. Run-timing 
designation at the Feather River Hatchery is more complicated but is managed at a fine-scale by hatchery practices, 
where early returning fish in May and April (expressing the Spring-run life history) are visibly tagged and re-released 
to the river. Subsequently in the Fall, when hatchery raceways are reopened, only fish with the visible tag are included
as Spring-run broodstock. Individual-based analyses of RoSA genotypes have demonstrated
